---
title: "HW_241106"
author: "Hana Kwon"
date: "2024-11-06"
output: 
  pdf_document:
    latex_engine: lualatex
---

#### **[POLS4720] 'Applied Regression & Causal Inference'**

# **Homework**

### **by Hana Kwon**

------------------------------------------------------------------------

### [**Class 9b: Poststratification and missing-data imputation**]{.underline} **- Chapter 17**

**1.**

**1-a.**

```{r}
# Defining the data
effects <- c(2.5, -0.9, 1.9)  # effects for 6th, 7th, and 8th grades
se <- c(1.1, 1.5, 1.2)        # standard errors for each grade
weights <- c(0.35, 0.35, 0.30) # population weights

# Population average effect
average_effect <- sum(weights * effects)

# Standard error calculation
var <- sum((weights * se)^2)
se_pop <- sqrt(var)

average_effect
se_pop

##Answer: The estimated population average effect is r average_effect (1.13) with a standard error of r se_pop(0.744)
```

**1-b.**

```{r}
# Given values for 6th and 7th grades and total pop effect
effects_known <- c(3.5, -1.9) # Known effects
se_known <- c(2.1, 2.5)       # Known SEs
weights_known <- c(0.35, 0.35) # Known weights

# Solving for X and Y using algebra (establishing equations)
average_target <- 2.0  # Given average effect for pop
se_target <- 3.5       # Given SE for pop

# Calculating required effect for 8th grade
effect_8 <- (average_target - sum(weights_known * effects_known)) / 0.3

# Solving for required SE for 8th grade
var_target <- se_target^2
var_8 <- (var_target - sum((weights_known * se_known)^2)) / 0.3^2
se_8 <- sqrt(var_8)

effect_8
se_8

##Answer: The values of ð‘‹and Y for the eighth grade are r effect_8 (4.8) and r se_8(11.03), respectively.
```

**2.**

**2-a.\
**

```{r}
# Complete-case analysis includes rows where y and z are observed for regression of y on z
complete_case_y_z <- c(8, 9, 10)  # Rows with no missing y and z values

# For regression of y on x and z, all x, y, z must be present
complete_case_y_x_z <- integer(0)  # No row has complete x, y, z

complete_case_y_z
complete_case_y_x_z

###Answer: 
##For a regression of y on z, rows 8, 9, and 10 are included in the complete-case analysis.
##For y on x and z, no rows are included in the complete-case analysis, as no rows have complete values for x, y, and z simultaneously.
```

**2-b.**

```{r}
# Available-case analysis for y on z includes rows with any non-missing y and z
available_case_y_z <- c(2, 8, 9, 10)

# Available-case analysis for y on x and z includes rows with any non-missing x, y, z
available_case_y_x_z <- c(6, 7, 8, 9, 10)  # Rows with available y and z (not necessarily x)

available_case_y_z
available_case_y_x_z

##Answer:
##For a regression of y on z, the available-case analysis includes rows 2, 8, 9, and 10.
##For a regression of y on x and z, the available-case analysis includes rows 6, 7, 8, 9, and 10.
```

------------------------------------------------------------------------

**3.**

5 reasons why we might expect the estimated effect in future studies to be lower than in initial studies?

1.  **Regression to the Mean**: Initial studies may capture an unusually strong effect due to chance, which diminishes in later studies.

2.  **Selection Bias**: Early studies might focus on contexts where the treatment effect is likely to be strongest, while later studies could have a broader, less favorable sample.

3.  **Publication Bias**: Early, significant findings are more likely to be published, while null or less significant results in subsequent studies are underreported.

4.  **Methodological Improvements**: Initial studies might not control for all confounding variables, leading to overestimation, while later studies improve upon these methods.

5.  **Natural Decline in Novelty Effects**: A new treatment or intervention might initially have strong effects due to novelty or enthusiasm, which decline over time as it becomes routine.

------------------------------------------------------------------------

**4. In Pairs**

```{r}
library(rstanarm)
set.seed(123)

n <- 10

ERS <- runif(n, 50, 100)
GDP <- runif(n, 1e6, 1e7)
Infla <- runif(n, 0, 12)
policy_treat <- sample(rep(c(0, 1), c(n/2, n/2)), n)

coef_ERS <- 0.3
coef_treat <- 4
coef_GDP <- 1e-10
coef_Infla <- -0.3

FDI <- coef_ERS * ERS + coef_treat * policy_treat + 
  coef_GDP * GDP + Infla * coef_Infla

fake <- data.frame(ERS, GDP, Infla, policy_treat, FDI)

fake$standard_ERS <- scale(ERS)
fake$standard_FDI <- scale(FDI)

groupby_treat <- split(fake$standard_FDI, fake$policy_treat)

sd_groups <- apply(as.data.frame(groupby_treat),
                   2, sd)

print(sd_groups)

fit <- stan_glm(standard_FDI ~ standard_ERS + policy_treat, data = fake,
                refresh = 0)
print(fit)
```
