---
title: "HW_241030"
author: "Hana Kwon"
date: "2024-10-30"
output: pdf_document
latex_engine: xelatex
geometry: margin=1in
---

#### **[POLS4720] 'Applied Regression & Causal Inference'**

# **Homework**

### **by Hana Kwon**

------------------------------------------------------------------------

### [**Class 8b:Working with logistic regression**]{.underline} **- Chapter 14**

**1.**

**1-a.**

$Pr(y = 1) = \frac{1}{1 + e^{-(−2 + 3x)}}$

```{r}
# Define function for logistic probability
logit <- function(z) {
  1 / (1 + exp(-z))
}

# Generate values for x and calculate Pr(y = 1)
x <- seq(0, 5, length.out = 100)
p_y_1 <- logit(-2 + 3 * x)

# Plot the curve
plot(x, p_y_1, type = "l", col = "blue", lwd = 2,
     ylab = "Pr(y = 1)", xlab = "x",
     main = expression("Pr(y = 1) = logit^{-1}(-2 + 3 * x)"))
```

**1-b.**

Here, the logistic function is modified by the term involving (z):

$Pr(y = 1) = \frac{1}{1 + e^{-(−2 + 3x - 3z)}}$

```{r}
# Set values of z
z_values <- c(0, 1, 2)
colors <- c("blue", "red", "green")

# Plot the curve for different values of z
plot(x, logit(-2 + 3 * x - 3 * z_values[1]), type = "l", col = colors[1], lwd = 2,
     ylab = "Pr(y = 1)", xlab = "x",
     main = expression("Pr(y = 1) = logit^{-1}(-2 + 3 * x - 3 * z)"))

# Add lines for z = 1 and z = 2
for (i in 2:3) {
  lines(x, logit(-2 + 3 * x - 3 * z_values[i]), col = colors[i], lwd = 2)
}

# Add legend
legend("bottomright", legend = paste("z =", z_values), col = colors, lwd = 2)
```

**2.**

**2-a.\
**The model: $Pr(y = 1) = \frac{1}{1 + e^{-(−0.2 + 0.3x - 1.5z -0.xz)}}$

For each ( z ):

-   (z=0):

    $Pr(y = 1) = \frac{1}{1 + e^{-(−0.2 + 0.3x)}}$

-   (z=1):

    $Pr(y = 1) = \frac{1}{1 + e^{-(−0.2 + 0.3x - 1.5 -0.2x)}}$

-   (z=2):

    $Pr(y = 1) = \frac{1}{1 + e^{-(−0.2 + 0.3x - 3 -0.4x)}}$

**2-b.**

```{r}
# Model with z-values 0, 1, 2
plot(x, logit(-0.2 + 0.3 * x), type = "l", col = colors[1], lwd = 2,
     ylab = "Pr(y = 1)", xlab = "x",
     main = expression("Pr(y = 1) = logit^{-1}(-0.2 + 0.3 * x - 1.5 * z - 0.2 * x * z)"))

# Plot for each z = 1, z = 2
lines(x, logit(-0.2 + 0.3 * x - 1.5 - 0.2 * x), col = colors[2], lwd = 2)
lines(x, logit(-0.2 + 0.3 * x - 3 - 0.4 * x), col = colors[3], lwd = 2)

# Legend
legend("bottomright", legend = paste("z =", z_values), col = colors, lwd = 2)
```

**2-c.**

\>\> From the equations above, the three curves will intersect where the effects of (z) terms cancel each other out.

\>\> We are working with the logistic regression model:

$Pr(y = 1) = \frac{1}{1 + e^{-(−0.2 + 0.3x - 1.5z -0.2xz)}}$with x in the range (0, 10) and z taking values 0, 1, and 2 .

1.  **To determine the crossing point**, we can set up equations where the curves for different values of  z  intersect:
    -   For curves with  z = 0 ,  z = 1 , and  z = 2 , we equate their probabilities by finding  x  where their logit functions match.
2.  **Solve these equations**: Setting the logit transformations equal gives insight into where these curves may cross.

\>\> **Why They Cross**? : The crossing point for logistic models with interaction terms often occurs at a particular value of  x  where the combined effect of  x  and  z  leads to similar predicted probabilities. For this model, we’d expect that certain values of  x  will yield similar results across  z , balancing out the coefficients in the model’s linear predictor.

**3. In Pairs**

```{r}
library(tidyverse)
library(rstanarm)
library(arm)

ipe_data <- readRDS("~/Desktop/2)Causal Inference/In Pair/4. Graham_Tucker_IPE_v5.RDS")

filtered_data <- ipe_data %>%
  dplyr::select(year, country, exchange_rate_stable_TR, fdiflows_UNCTAD, gdppc_WDI) %>%
  filter(year >= 1980 & year <= 2000) %>%
  filter(!is.na(exchange_rate_stable_TR) & is.finite(exchange_rate_stable_TR))

filtered_data$threshold <- ifelse(filtered_data$fdiflows_UNCTAD > 1871.1, 1, 0)

fit <- stan_glm(threshold ~ exchange_rate_stable_TR,
                data = filtered_data, family = binomial(link = "logit"),
                refresh = 0)

print(fit)

x_value <- seq(min(filtered_data$exchange_rate_stable_TR), 
               max(filtered_data$exchange_rate_stable_TR), by = 0.02)
coefficients <- coef(fit)
log_odds <- coefficients[1] + coefficients[2] * x_value
predicted_probability <- invlogit(log_odds)

predicted_data <- data.frame(exchange_rate = x_value, probability = predicted_probability)

predicted_data %>%
  ggplot(aes(x = exchange_rate, y = probability)) +
  geom_point() +
  geom_line() +
  labs(x = "x", y = "Probability of y = 1")
```

------------------------------------------------------------------------

### [**Class 9a:**]{.underline} [**Design and sample size decisions**]{.underline} **- Chapter 15**

**1.**

**1-a.** 80% Power for 95% Significance Level

\>\> To calculate sample size \\( n \\) for 80% power at a 95% significance level,

```{r}
# Given values
sigma <- 20.1
effect_size <- 5.0
alpha_95 <- 0.05
beta <- 0.2

# Z-scores for 95% significance and 80% power
z_alpha <- qnorm(1 - alpha_95 / 2)
z_beta <- qnorm(1 - beta)

# Calculate sample size
n_95 <- ((sigma / effect_size) * (z_alpha + z_beta))^2
n_95
```

**1-b.** 80% Power for 90% Significance Level

Similarly, for a 90% significance level:

```{r}
# Adjust alpha for 90% significance level
alpha_90 <- 0.1
z_alpha_90 <- qnorm(1 - alpha_90 / 2)

# Calculate sample size
n_90 <- ((sigma / effect_size) * (z_alpha_90 + z_beta))^2
n_90
```

------------------------------------------------------------------------

**2.**

**2-a.** Estimating U.S. Population Support for Death Penalty to ±3% Margin of Error

For a proportion estimate with a standard error of ±3% at 95% confidence:

```{r}
# Margin of error and critical Z-value
margin_error <- 0.03
z_value_95 <- qnorm(1 - 0.05 / 2)

# Sample size calculation
n_death_penalty <- (z_value_95 / margin_error)^2 * 0.5 * 0.5
n_death_penalty
```

**2-b.** Estimating Latino Support for Death Penalty

With 14% of the U.S. population being Latino, we calculate the sample size for a ±3% margin within the Latino population.

```{r}
# Latino proportion in the population
latino_prop <- 0.14

# Adjusted sample size for Latino population proportion
n_latino_death_penalty <- (z_value_95 / margin_error)^2 * latino_prop * (1 - latino_prop)
n_latino_death_penalty
```

**2-c.** Estimating Latino Population Proportion to ±1% Margin

To estimate the proportion of Latinos within the U.S. population to a ±1% margin:

```{r}
# Margin of error for Latino population proportion
margin_error_latino <- 0.01

# Sample size calculation
n_latino_proportion <- (z_value_95 / margin_error_latino)^2 * 0.5 * 0.5
n_latino_proportion
```

------------------------------------------------------------------------

**3.** Election Poll Sample Size Calculation

\>\> In an election scenario with candidates A, B, and C having estimated support levels of 45%, 35%, and 20%, we estimate the sample size needed to assess the difference between candidates A and B within ±5 percentage points.

```{r}
# Margin of error for difference
margin_error_ab <- 0.05

# Pooled proportion for two candidates A and B
p_a <- 0.45
p_b <- 0.35
p_pooled <- (p_a + p_b) / 2

# Sample size calculation
n_election <- (z_value_95 / margin_error_ab)^2 * p_pooled * (1 - p_pooled)
n_election
```
