---
title: "section_sept_27"
author: "Elden Griggs"
date: "`r Sys.Date()`"
output: pdf_document
---
```{r}
rm(list = ls())
library(glue)
library(tidyverse)
## me building the data
# read_csv("hogwarts_admits.csv") %>% #name and address only
#   dplyr::select(name,address ) %>%
#   mutate(father_wizard = rbinom(n(), 1, .5)) %>%
#   mutate(mother_wizard = rbinom(n(), 1, if_else(father_wizard == 1, .8, .2))) %>%
#   mutate(family_gringotts_account_size= 3*mother_wizard + 3*father_wizard + 1.5*rnorm(n()) ) %>%
#   mutate(family_gringotts_account_size = if_else((mother_wizard ==0 & father_wizard == 0 )|family_gringotts_account_size <0, 0,family_gringotts_account_size)*10000)  %>%
#   mutate(quiditch_capabilities = round(rnorm(n(), 3 + 2*family_gringotts_account_size/10000 + mother_wizard + father_wizard , 5 ))) %>%
#   mutate(quiditch_capabilities = case_when(quiditch_capabilities < 0 ~ 0,
#                                           quiditch_capabilities > 30 ~ 30,
#                                           .default = quiditch_capabilities)) %>%
#   mutate(parseltongue = rbinom(n(), 1, .05)) %>%
#   write_csv("hogwarts_admits.csv")
```

### Hogwarts Admininstrative Unit and Coding

### data checking
```{r}
hogwarts_admits <- read_csv("hogwarts_admits.csv") 
## show me a character vector 

## provide me with a list of the names and addresses also add the data into this list and add another list with a character note inside of it

hogwarts_list <- list(hogwarts_admits$name, hogwarts_admits$address, hogwarts_admits, list(note))
note <- "this is a hogwarts list"
## what is the difference between a matrix, data.frame/tibble and a list?

```


### letter writing
```{r}
letter_base_text<- "
HOGWARTS SCHOOL of WITCHCRAFT and WIZARDRY

To {name}
{address}

Headmaster: Albus Dumbledore
(Order of Merlin, First Class, Grand Sorc., Chf. Warlock,
Supreme Mugwump, International Confed. of Wizards)


Dear {name},
We are pleased to inform you that you have been accepted at Hogwarts School of Witchcraft and Wizardry. Please find enclosed a list of all necessary books and equipment.
Term begins on 1 September. We await your owl by no later than 31 July.
Yours sincerely,
Minerva McGonagall
Deputy Headmistress"



```


### challenge make an admission letter generator that takes a name, address and then prints the letter. Use a random admit to test it
```{r}
add_function <- function(first_number =2 , second_number = 3) {
  first_number + second_number
}
add_function()
add_function(first_number=4)
#`+`(2+3) even things you take for granted as functions are functions
## hint look at paste0 and paste
```

### answer
```{r}
hogwarts_admits <- hogwarts_admits  %>% 
  separate(col = "name", into = c("last_name", "first_name"), sep = ",")





class_letter_generator<- function(name, address) {
  first_part <- "HOGWARTS SCHOOL of WITCHCRAFT and WIZARDRY

To"
 second_part <-  "Headmaster: Albus Dumbledore
(Order of Merlin, First Class, Grand Sorc., Chf. Warlock,
Supreme Mugwump, International Confed. of Wizards)


Dear"
last_part <-  "We are pleased to inform you that you have been accepted at Hogwarts School of Witchcraft and Wizardry. Please find enclosed a list of all necessary books and equipment.
Term begins on 1 September. We await your owl by no later than 31 July.
Yours sincerely,
Minerva McGonagall
Deputy Headmistress"
  paste(first_part, name, address,second_part, name, last_part)
}

class_letter_generator("tom", "columbia")

hogwarts_letter_generator <- function(first_name, last_name, address) {
   letter <-glue("
HOGWARTS SCHOOL of WITCHCRAFT and WIZARDRY

To {first_name} {last_name}
{address}

Headmaster: Albus Dumbledore
(Order of Merlin, First Class, Grand Sorc., Chf. Warlock,
Supreme Mugwump, International Confed. of Wizards)


Dear{first_name} {last_name},
We are pleased to inform you that you have been accepted at Hogwarts School of Witchcraft and Wizardry. Please find enclosed a list of all necessary books and equipment.
Term begins on 1 September. We await your owl by no later than 31 July.
Yours sincerely,
Minerva McGonagall
Deputy Headmistress")
   return(letter)
}

test_subject <- hogwarts_admits %>% 
  slice_sample(n = 1)

hogwarts_letter_generator(test_subject$first_name, test_subject$last_name, test_subject$address)

```
### Challenge write all the letters! Please write all the letters to Hogwarts admits and save them to txt files on your computer in a folder
```{r}
test <- c(1:24)
for (i in test) {
  print(letter)
}
for (i in 1:24){
  print(letters[l])
}
# hint check writelines also
```

### answer
```{r}
for (student_number in 1:23){
  letter_for_student <- hogwarts_letter_generator(first_name = hogwarts_admits[[student_number,2]],
                                                    last_name = hogwarts_admits[[student_number,1]], 
                                                    address = hogwarts_admits[[student_number,3]])
  hogwarts_student_letters_directory <- "hogwarts_student_letters_directory" 
  letter_path <- glue("{hogwarts_student_letters_directory}/hogwarts_letter_student{student_number}.txt")
  if (dir.exists(hogwarts_student_letters_directory)) {
    write_lines(letter_for_student, letter_path)
  } else {
    dir.create("hogwarts_student_letters_directory")
    write_lines(letter_for_student, letter_path)
  }
  
}
```


### whiling away and sending the letters

```{r}
n <- 0
while (n< 10) {
  n <- n + 1
  print(n)
}
# hint check file.remove() and list.files()
```

### challenge use the while loop and delete all the letters in your folder

```{r}
while (length(list.files("hogwarts_student_letters_directory"))>0) {
  file_sent_by_deletion <- sample(list.files("hogwarts_student_letters_directory"),1)
  letter_path <- glue("{hogwarts_student_letters_directory}/{file_sent_by_deletion}")
  file.remove(letter_path)
}
## note the below with recursive does the above
if (length(list.files("hogwarts_student_letters_directory"))==0){
  unlink("hogwarts_student_letters_directory", recursive=TRUE)
}
```

### setting up your grades
```{r}
# library(MASS)
# 
# set.seed(123)
# random_matrix <- matrix(runif(49, min = -10, max = 10), nrow = 7)
# 
# cov_matrix <- t(random_matrix) %*% random_matrix
# 
# mu_vector <- runif(7, min = 0, max = 100)
# 
# grades <- as_tibble(abs(round(mvrnorm(23, mu = mu_vector, Sigma = cov_matrix))))
# names(grades) <- c("transfiguration_final_grade",
#          "charms_final_grade",
#          "potions_final_grade",
#          "history_of_magic_final_grade",
#          "defence_against_the_dark_arts_final_grade",
#          "astronomy_final_grade",
#          "herbology_final_grade")
# hogwarts_admits %>%
#   dplyr::select(name) %>%
#   bind_cols(grades) %>%
#   mutate(across(contains("final_grade"), ~ if_else(. > 100, 100, .))) %>% 
#   mutate(house = sample(c("Gryffindor", "Hufflepuff", "Ravenclaw", "Slytherin"), n(), replace = TRUE)) %>% 
#   write_csv("hogwarts_final_grades.csv")
# 

```

### get me a regression summary for transfiguration final grade on each other class (transfiguration final grade~ some grade). Additionally get me a plot of each relationship with line and scatter points. Color the points by house. Output each summary and graph pair into a list. This list should be length 6. If you want a challenge, get me all combinations of variables. This should be length 42. 
```{r}
hogwarts_final_grades <- read_csv("hogwarts_final_grades.csv")

```

### answer
```{r}


get_plot <- function(x_var, y_var) {
  grade_plot <- ggplot(data = hogwarts_final_grades, aes_string(x = x_var, y = y_var, color = "house")) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE, color = "black") +
    scale_colour_manual(values = c("#ae0001","#f0c75e", "#222f5b", "#2a623d")) +
    theme_minimal()
}
library(broom)
get_lm <- function(x_var, y_var) {
  lm_data <- lm(as.formula(glue("{y_var}~{x_var}")), data = hogwarts_final_grades) %>% 
    tidy()
}
get_list <- function(x_var, y_var) {
  plot_for_relationship <- get_plot(x_var, y_var) 
  lm_information_data <- get_lm(x_var, y_var)
  return(list(plot_for_relationship, lm_information_data))
}

simple_list <- names(hogwarts_final_grades[3:8])

simple_challenge <- map(simple_list, ~get_list(.x, "transfiguration_final_grade"))

combinations <- crossing(first_var= names(hogwarts_final_grades[2:8]), second_var= names(hogwarts_final_grades[2:8])) %>% 
  filter(first_var!=second_var)

boss_challenge <- map2(combinations$first_var, combinations$second_var, ~get_list(.x, .y))

simple_challenge[1]
boss_challenge[1]



```

###lapply, map, for loops! Why!
```{r}
# r inferno example https://www.burns-stat.com/pages/Tutor/R_inferno.pdf
# good discussion of perfomance differences here https://stackoverflow.com/questions/42393658/what-are-the-performance-differences-between-for-loops-and-the-apply-family-of-f
x <- 10
lsum <- 0
for(i in 1:length(x)) {
lsum <- lsum + log(x[i])
}
# the above is generally seen as less preferable than the below
lsum <- sum(log(x))


###### examples borrowed from slack conversation
n <- 10000

result_for <- list()
for (i in 1:n) {
result_for[[i]] <- i^2
}

result_lapply <- lapply(1:n, function(x) x^2)

result_prealloc <- vector('list', n)
for (i in 1:n) {
  result_prealloc[[i]] <- i^2
  }
result_prealloc



```



### regression questions with quiditch and grades

```{r}
hogwarts_total <- hogwarts_admits %>% 
  left_join(hogwarts_final_grades, by = "name")

lm(quiditch_capabilities~1, data = hogwarts_total)
lm(quiditch_capabilities~1+family_gringotts_account_size, data = hogwarts_total)
lm(quiditch_capabilities~family_gringotts_account_size, data = hogwarts_total)
lm(quiditch_capabilities~family_gringotts_account_size-1, data = hogwarts_total)
lm(quiditch_capabilities~0 + family_gringotts_account_size , data = hogwarts_total)
lm(quiditch_capabilities~ (family_gringotts_account_size + transfiguration_final_grade)^2 , data = hogwarts_total)
lm(quiditch_capabilities~ family_gringotts_account_size + transfiguration_final_grade + transfiguration_final_grade:family_gringotts_account_size , data = hogwarts_total)
lm(quiditch_capabilities~ family_gringotts_account_size*transfiguration_final_grade , data = hogwarts_total)
lm(quiditch_capabilities~ (family_gringotts_account_size + transfiguration_final_grade)^2 , data = hogwarts_total)
lm(quiditch_capabilities~ poly(family_gringotts_account_size,2) + transfiguration_final_grade , data = hogwarts_total)
lm(quiditch_capabilities~ I(family_gringotts_account_size^2) + transfiguration_final_grade , data = hogwarts_total)

```


